My title

### 2024-01-21 outputs/paper/paper.qmd
Loaded the tidyverse package in the paper.qmd file

# Data

@@

>>>>

```{r}
#### Loading Packages ####

# install.packages("tidyverse")
library(tidyverse)
```

# Introduction {#introduction}

# Data {#data}

@@

## Visualizing the data

```{r}
#### Creating Tables and Graphs ####

# Loading the cleaned dataset

# outbreak_cleaned_data <- read_csv("outputs/data/cleaned_data.csv")

# Creating a graph to depict the number of outbreaks by location type

#| label: num-outbreaks-by-location
#| fig-cap: Number of Toronto healthcare outbreaks by type of location in 2023
#| echo: false

# Obtaining the number of outbreaks by type of location
# The knowledge used to write this code was gained in STA304H1.

```
